%-------------------------
% Resume in Latex
% Author : Sujit Joshi
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
 }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Sujit Joshi}} & Email : \href{mailto:joshi.sujit020386@gmail.com}{joshi.sujit020386@gmail.com}\\
   & Mobile : \href{tel:+5407246588}{+1-540-724-6588} \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {George Mason University}{Fairfax, VA}
      {Master of Science in Computer Science; GPA 3.7}{Aug. 2009 -- May. 2011}
    \resumeSubheading
      {Datta Meghe College of Engineering}{Navi Mumbai, India}
      {Bachelor of Engineering in Information Technology; GPA 3.7}{Aug. 2003 -- July. 2007}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {TNS Inc}{Reston, VA}
      {Software Engineer 4}{Mar 2018 - Present}
      \resumeItemListStart
        \resumeItem{Owner of web portal called Oculus}
          {Responsible for owning financial division's offering called Oculus.}
        \resumeItem{ETL}
          {Extract-transform-load metrics from multi-regional devices.}
        \resumeItem{Oculus - Web portal}
          {Display metrics in user-customizable dashboards. Also used for user management, device management, etc.}
          \resumeItem{Alerts}
          {Allow users to create alerts based on a criteria that they can define.}
          \resumeItem{CI/CD}
          {Integrate the project with Gitlab cloud using Docker executor.}
          \resumeItem{Dockerized projects}
          {Dockerized most of the tools used within the company.}
      \resumeItemListEnd
      \textbf{Languages/Technologies used}{: Spring Boot, Hibernate, Influx, Chronograf, Kafka, Kafka Streams, Apache Flink, Apache Geode (distributed cache), Highcharts, Smartclient UI (by Isomorphic Software), Vue 3, Quasar, Keycloak}

    \resumeSubheading
      {Successfactors, an SAP Company}{Reston, VA}
      {Senior Software Engineer}{May 2014 - Mar 2018}
      \resumeItemListStart
        \resumeItem{Upgrade BIRT}
          {Upgraded the reporting framework called Business Intelligent and Reporting Tools (BIRT) which not just improved the build process but also gave customers many new reporting features.}
        \resumeItem{Offline Player}
          {Offline Player allowed users to finish courses offline. Their progress was synced later then they got online.}
        \resumeItem{SME for BIRT reports}
          {Point of contact for all reporting issues customers faced.}
      \resumeItemListEnd
      \textbf{Languages/Technologies used}{: Java, Spring, Hibernate, Install4j, Odata}

    \resumeSubheading
      {Overture Inc.}{Bethesda, MD}
      {Software Engineer}{Jan 2011 - May 2014}
      \resumeItemListStart
        \resumeItem{Moss}
          {Implemented instant mortgage upload functionality which allows users to import loans when they login and not wait for the nightly import scripts. Also used Java POI, a Java API for Mircosoft Documents. The imported loans were used by company's propriety rule engine called Maestro.}
        \resumeItem{MODM}
        {Mapped data files in XML and Excel to MISMO (format widely used in mortgage processing firms) templates.}
        \resumeItem{BIRT}
        {Integrated Business Intelligent and Reporting Tools (BIRT) in Moss and MODM.}
      \resumeItemListEnd
      \textbf{Languages/Technologies used}{: Java, Spring, Hibernate, XML}
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------

\section{Side Projects}
  {Druid, a Rust native, platform independent GUI toolkit}
    \begin{itemize}
      \item {\href{https://github.com/linebender/druid/pull/2172}{Introduce intrinsic widget: Widgets that expand/shrink based on its contents.}}
      \item {\href{https://github.com/linebender/druid/pull/2087}{Dropdown widget: Widgets that are overlayed on main window.}}
    \end{itemize}  

%-------------------------------------------
\end{document}
